Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-24 journal/article.tex
Large scale

Laanti 2008:
[2] Kähkönen Tuomo, “Agile Methods for large organizations – building communities of practice”.
Proc. Agile Development Conf. (ADC), 2004, pp. 2-10.

[7] Eckstein Jutta, “Agile Software Development in the large: Diving into the deep”,
Dorset House Publishing, 2004. ISBN 0-932633-57-9.
[8] Leffingwell Dean, “Scaling Software Agility: Best Practices for Large Enterprises”,
Addison-Wesley Professional, 2007. ISBN-10: 0321458192.
[12] Highsmith J., Agile for the Enterprise, “From Agile Teams to Agile Organizations”,
Cutter, 2005. http://www.cutter.com/program/ fulltext/reports/2005/01/index.html .
[13] Schwaber Ken, “Enterprise and Scrum”, Microsoft Press 2007, ISBN-10: 0735623376.

@@

The following research questions were set to guide the research process.

@@

Proceeding a workshop at XP2013 \cite{Dingsoyr2013a} Dingsøyr et al.
compiled a description of the definition of large scale \cite{Dingsoyr2013b}.
Dingsøyr et al. describe that at the XP2013 workshop the most common view on
large scale was the involvment of many people \cite{Dingsoyr2013b}. Dingsøyr et
al. conducted a brief literature search to identify what definitions on large
scale are used. The results showed that large scale had been regadred in terms
of size in persons or teams, project budget, code base size, and project
duration.
Paasivaara et al. \cite{Paasivaara2008} referred to an organization of 40 people
and 7 teams. Berger and Beynon-Davies \cite{Berger2009} present the project cost
of over £10 million as a factor of large scale, but also highlight a team size
of over 50 people. A product with a code base size of over 5 million lines of
code was considered to represent a large scale development effort by Petersen
and Wohlin \cite{Petersen2010}. A project time of 2 years was considered as a
factor of large scale by Bjarnson et al. \cite{Bjarnason2011}, as well as a
project scope of 60-80 features.

----

Moore and Spens \cite{Moore2008} define large scale global development in the
scope of their research as 300 people across 3 sites.

----

--> What will bring complexity into software? Not costs or the length of the
    schedule. --> Having many people will bring the complexity in terms of the
    SDM to use.

--> [Cockburn 2003] Agile is best suitable for teams around 50 people or fewer.
--> Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
    Perplexed: Addison-Wesley, 2003. --> There might be a 50 person boundary?
    --> See Boehm also for list of

--> The company must already be with N teams or N people, not growing up to the
    required numbers. Small companies in growth are therefore excluded.

@@

\begin{table}[b]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.56\textwidth}
                     >{\raggedright\arraybackslash}p{0.36\textwidth} }
        \toprule
        Challenges relating to large scale  &  Described in \\
        \midrule
        Management roles unclear in agile       &  P2, P11, P27, P30, P38, P49, P52 \\
        Using old and new models side by side   &  P1, P8, P10, P26, P29 \\
        Management uses waterfall model         &  P3, P6,P35,P38, P45, P46  \\
        Duplicating management with two models  &  P20, P48 \\
        Agile models diverge between teams      &  P8, P9, P38, P43, P48 \\
        Internal boundaries in organization     &  P10, P11 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of challenges relating especially to large scale}
    \label{table:challenges_largescale}
\end{table}

>>>>

Laanti 2008:
[2] Kähkönen Tuomo, “Agile Methods for large organizations – building communities of practice”.
Proc. Agile Development Conf. (ADC), 2004, pp. 2-10.
[7] Eckstein Jutta, “Agile Software Development in the large: Diving into the deep”,
Dorset House Publishing, 2004. ISBN 0-932633-57-9.
[8] Leffingwell Dean, “Scaling Software Agility: Best Practices for Large Enterprises”,
Addison-Wesley Professional, 2007. ISBN-10: 0321458192.
[12] Highsmith J., Agile for the Enterprise, “From Agile Teams to Agile Organizations”,
Cutter, 2005. http://www.cutter.com/program/ fulltext/reports/2005/01/index.html .
[13] Schwaber Ken, “Enterprise and Scrum”, Microsoft Press 2007, ISBN-10: 0735623376.

Vlaanderen 2012:
22. Sidky, A.S.: A Structured Approach to Adopting Agile Practices: The Agile Adop-
tion Framework (June 2007)

Cockburn 2003:
R. Crocker, Large-Scale Agile Software Development, Addison-Wesley, 2003.

@@

The following research questions were set to guide the research.

@@

The definition of large scale was discussed in a workshop at XP2013
\cite{Dingsoyr2013a}. Proceeding the workshop, Dingsøyr et al.
compiled a description of the definition of large scale \cite{Dingsoyr2013b}.
The most common view in the XP2013 workshop was that the involvment of many
people is the main factor in large scale \cite{Dingsoyr2013b}.

Dingsøyr et al. conducted a brief literature search to identify what definitions
on large scale are used \cite{Dingsoyr2013b}. The results showed that large
scale had been regadred in terms of size in persons or teams, project budget,
code base size, and project duration. As examples from the results, Paasivaara
et al. \cite{Paasivaara2008} referred to an organization of 40 people and 7
teams. Berger and Beynon-Davies \cite{Berger2009} present the project cost of
over £10 million as a factor of large scale, but also highlight a team size of
over 50 people. A product with a code base size of over 5 million lines of code
was considered to represent a large scale development effort by Petersen and
Wohlin \cite{Petersen2010}. A project time of 2 years was considered as a factor
of large scale by Bjarnson et al. \cite{Bjarnason2011}, as well as a project
scope of 60-80 features.

As a part of our research, we identified further definitions of large scale. All
of these definitions referred to the number of people involved.
In early work on agile Fowler \cite{Fowler2000} regards the Crystal methodology
being suitable for up to 50 people, thus setting a boundary beyond which agile
methods would be expected to need special considerations. Also Williams and
Cockburn \cite{Williams2003} present 50 people as a limit which practicioners
and researchers has seen as the largest organization suitable for agile.
Elshamy and Elssamadisy \cite{Elshamy2006} considered a development project
large if it had a staff between 50 and 100 people, including all project
personnel. Finally, the largest numbers were presented by Moore and Spens
\cite{Moore2008} who define large scale in the scope of their research as 300
people across 3 sites.

Based on these findings we defined large scale in the scope of this research to
denote organizations with 50 or more people. These 50 people would not all need
to be developers, but they should be part of the development organization. For
instance, Scrum masters and software architects would be counted in. As some
studies presented the number of teams rather than number of people, we
correspondignly defined large scale to denote development efforts involving at
least 6 teams. Having 6 teams with an average teams size of 6 people, plus a
number of supporting staff, can reasonably be considered to form an organization
of 50 people.

% --> What will bring complexity into software? Not costs or the length of the
%     schedule. --> Having many people will bring the complexity in terms of the
%     SDM to use.
% 
% --> Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
%     Perplexed: Addison-Wesley, 2003. --> There might be a 50 person boundary?
%     --> See Boehm also for list of

% --> The company must already be with N teams or N people, not growing up to the
%     required numbers. Small companies in growth are therefore excluded.

@@

\begin{table}[b]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.56\textwidth}
                     >{\raggedright\arraybackslash}p{0.36\textwidth} }
        \toprule
        Challenges relating to large scale  &  Described in \\
        \midrule
        Management roles unclear in agile       &  P2, P11, P27, P30, P38, P49, P52 \\
        Using old and new models side by side   &  P1, P8, P10, P26, P29 \\
        Management uses waterfall model         &  P3, P6, P35, P38, P45, P46 \\
        Duplicating management with two models  &  P20, P48 \\
        Agile models diverge between teams      &  P8, P9, P38, P43, P48 \\
        Internal boundaries in organization     &  P10, P11 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of challenges relating especially to large scale}
    \label{table:challenges_largescale}
\end{table}
